Future Directions

### 2021-02-28 manuscripts/laplacian_smoothing/AISTATS/supplement_minimax_optimal_laplacian_smoothing.tex
Typos and copyedits

\onecolumn	
\aistatstitle{Supplementary Materials for ``Minimax Optimal Regression over Sobolev Spaces via Laplacian Regularization on Neighborhood Graphs''}

@@

Now we explain why the particular choice of representative is not crucial, using the notion of a Lebesgue point. Recall that for a locally Lebesgue integrable function $f$, a given point $x \in \mc{X}$ is a \emph{Lebesgue point} of $f$ if the limit of $1/(\nu(B(x,\varepsilon)))\int_{B(x,\varepsilon)} f(x) dx$ as $\varepsilon \to 0$ exists, and satisfies
\begin{equation*}
\lim_{\varepsilon \to 0} \frac{1}{\nu\bigl(B(x,\varepsilon)\bigr)} \int_{B(x,\varepsilon)} f(x) dx = f(x).
\end{equation*}
Let $E$ denote the set of Lebesgue points of $f$. By the Lebesgue differentiation theorem \citep{evans15}, if $f \in L^1(\mc{X})$ then almost every $x \in \mc{X}$ is a Lebesgue point, $\nu(\mc{X}\setminus E) = 0$. Since $f_0 \in H^1(\mc{X}) \subset \Leb^1(\mc{X})$, we can conclude that any function $g_0 \in f_0$ disagrees with the precise representative $f_0^{\star}$ only on a set of Lebesgue measure 0. Moreover, since we always assume the design distribution $P$ has a continuous density, with probability $1$ it holds that $g_0(X_i) = f_0^{\star}(X_i)$ for all $i = 1,\ldots,n$. This justifies the notation $f_0(X_i)$ that we use in our main text.

@@

\section{Graph-dependent error bounds}
\label{sec:fixed_graph_error_bounds}
In this section, we adopt the fixed design perspective; or equivalently, condition on $X_i = x_i$ for $i = 1,\ldots,n$. Let $G = \bigl([n],W\bigr)$ be a fixed graph on $\{1,\ldots,n\}$ with Laplacian matrix $\Lap = D - W$. The randomness thus all comes from the responses 
\begin{equation}
\label{eqn:fixed_graph_regression_model}
Y_i = f_{0}(x_i) + \varepsilon_i
\end{equation}
where the noise variables $\varepsilon_i$ are independent $N(0,1)$. In the rest of this section, we will mildly abuse notation and write $f_0 = (f_0(x_1),\ldots,f_0(x_n)) \in \Reals^n$. We will also write ${\bf Y} = (Y_1,\ldots,Y_n)$.

Recall~\eqref{eqn:laplacian_smoothing} and~\eqref{eqn:laplacian_smoothing_test}: the Laplacian smoothing estimator of $f_0$ on $G$ is
\begin{equation*}
\label{eqn:ls_G}
\wh{f} := \argmin_{f \in \Reals^n} \biggl\{ \sum_{i = 1}^{n}(Y_i - f_i)^2 + \rho \cdot f^{\top} \Lap f \biggr\} = (\rho \Lap + \Id)^{-1}{\bf Y}.
\end{equation*}
and the Laplacian smoothing test statistic is 
\begin{equation*}
\label{eqn:ls_ts_G}
\wh{T} := \frac{1}{n} \Bigl\|\wh{f}\Bigr\|_2^2.
\end{equation*}
We note that in this section, many of the derivations involved in upper bounding the estimation error of $\wh{f}$ are similar to those of \cite{sadhanala16}, with the difference being that we seek bounds in high probability rather than in expectation. We keep the work here self-contained for purposes of completeness.

\subsection{Error bounds for linear smoothers}
Let $S \in \Reals^{n \times n}$ be a square, symmetric matrix, and let 
\begin{equation*}
\wc{f} := SY
\end{equation*}
be a linear estimator of $f_0$. In  Lemma~\ref{lem:linear_smoother_fixed_graph_estimation} we upper bound the error $\frac{1}{n}\|\wc{f} - f_0\|_2^2$ as a function of the eigenvalues of $S$. Let $\lambdavec(S) = (\lambda_1(S),\ldots,\lambda_n(S)) \in \Reals^n$ denote these eigenvalues, and let $v_k(S)$ denote the corresponding unit-norm eigenvectors, so that $S = \sum_{k = 1}^{n} \lambda_k(S) \cdot v_k(S) v_k(S)^{\top}$. Denote $Z_k = v_k(S)^{\top} \varepsilon$, and observe that ${\bf Z} = (Z_1,\ldots,Z_n) \sim N(0,\Id)$.

@@

\textit{Variance.} Starting from~\eqref{pf:linear_smoother_fixed_graph_testing1} and recalling $\Var(Z_k^2) = 2$, we derive
\begin{equation}
\label{pf:linear_smoother_fixed_graph_testing_var}
\Var_{f_0}\bigl[\wc{T}\bigr] \leq 8 f_0^{\top} S^4 f_0 + 4 \sum_{k = 1}^{n} \bigl(\lambda_k(S)\bigr)^4.
\end{equation}

\textit{Bounding Type I and Type II error.} The upper bound~\eqref{eqn:linear_smoother_fixed_graph_testing_typeI} follows immediately from~\eqref{pf:linear_smoother_fixed_graph_testing_mean}, ~\eqref{pf:linear_smoother_fixed_graph_testing_var}, and Chebyshev's inequality.

The bound~\eqref{eqn:linear_smoother_fixed_graph_testing_typeII} also follows from Chebyshev's inequality, as can be seen by the following manipulations,
\begin{equation*}
\begin{aligned}
\Pbb_{f_0}\Bigl(\wc{T} \leq \wc{t}_b\Bigr) & = \Pbb_{f_0}\Bigl(\wc{T} - \Ebb_{f_0}\bigl[\wc{T}\bigr] \leq \wc{t}_b - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr) \\
& \overset{(i)}{\leq} \Pbb_{f_0}\Bigl(\Bigl|\wc{T} - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr| \geq \Bigl|\wc{t}_b - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr|\Bigr) \leq \frac{Var_{f_0}\bigl[\wc{T}\bigr]}{\bigl(\wc{t}_b - \Ebb_{f_0}\bigl[\wc{T}\bigr]\bigr)^2} \\ 
& \overset{(ii)}{\leq} 4 \frac{\Var_{f_0}\bigl[\wc{T}\bigr]}{(f_0^{\top} S^2 f_0)^2} \\
& \overset{(iii)}{\leq} \frac{32}{f_0^{\top} S^2 f_0} + \frac{4}{b^2} \\
& \overset{(iv)}{\leq} \frac{8}{b} \Biggl(\sum_{k = 1}^{n}\bigl(\lambda_k(S)\bigr)^4\Biggr)^{-1/2} + \frac{4}{b^2}
\end{aligned}
\end{equation*}
In the previous expression, $(i)$ and $(ii)$ follow since assumption~\eqref{eqn:linear_smoother_fixed_graph_testing_critical_radius} and equation~\eqref{pf:linear_smoother_fixed_graph_testing_mean} together imply 
\begin{equation*}
\wc{t}_b - \Ebb_{f_0}[\wc{T}] = f_0^{\top} S^2 f_0 - 2b\|{\bf \lambda}(S)\|_4^2 \geq \frac{1}{2}f_0^{\top} S^2 f_0
\end{equation*}
$(iii)$ follows from assumption~\eqref{eqn:linear_smoother_fixed_graph_testing_critical_radius} and the inequality~\eqref{pf:linear_smoother_fixed_graph_testing_var}, and $(iv)$ follows from~\eqref{eqn:linear_smoother_fixed_graph_testing_critical_radius}.

\subsection{Analysis of Laplacian Smoothing}
Upper bounds on the mean squared error of $\wh{f}$, and Type I and Type II error of $\wh{T}$, follow from setting $S = (\rho L + I)^{-1}$ in Lemmas~\ref{lem:linear_smoother_fixed_graph_estimation} and~\ref{lem:linear_smoother_fixed_graph_testing}. We give these results in Lemma~\ref{lem:ls_fixed_graph_estimation} and~\ref{lem:ls_fixed_graph_testing}, and prove them immediately. Recall that $\lambda_1,\ldots,\lambda_n$ are the $n$ eigenvalues of $\Lap$ (sorted in ascending order).
\begin{lemma}
	\label{lem:ls_fixed_graph_estimation}
	For any $\rho > 0$,
	\begin{equation}
	\label{eqn:ls_fixed_graph_estimation_prob}
	\frac{1}{n}\bigl\|\wh{f} - f_0\bigr\|_2^2 \leq \frac{2\rho}{n} \bigl(f_0^{\top} \Lap f_0\bigr) + \frac{10}{n}\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_{k} + 1\bigr)^2}
	\end{equation}
	with probability at least $1 - \exp\Bigl(-\sum_{k = 1}^{n}\bigl(\rho \lambda_k + 1\bigr)^{-2}\Bigr)$.
\end{lemma}
Recall that 
\begin{equation*}
\wh{t}_b := \frac{1}{n}\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k + 1\bigr)^2} + \frac{2b}{n}\sqrt{\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k + 1\bigr)^4}}.
\end{equation*}
\begin{lemma}
	\label{lem:ls_fixed_graph_testing}
	For any $\rho > 0$ and any $b \geq 1$, it holds that:
	\begin{itemize}
		\item \textbf{Type I error.}
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_typeI}
		\Pbb_0\Bigl(\wh{T} > \wh{t}_b\Bigr) \leq \frac{1}{b^2}
		\end{equation}
		\item \textbf{Type II error.} If
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_critical_radius}
		\frac{1}{n}\norm{f_0}_2^2 \geq \frac{2 \rho}{n} \bigl(f_0^{\top} \Lap f_0\bigr) + \frac{4b}{n} \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{1/2}
		\end{equation}
		then
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_typeII}
		\Pbb_{f_0}\Bigl(\wh{T}(G) \leq \wh{t}_b\Bigr) \leq \frac{4}{b^2} + \frac{8}{b} \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{-1/2}
		\end{equation}
	\end{itemize}
\end{lemma}
\paragraph{Proof of Lemma~\ref{lem:ls_fixed_graph_estimation}.}
Let $\wh{S} = (\Id + \rho \Lap)^{-1}$, the estimator $\wh{f} = \wh{S}Y$, and
\begin{equation*}
\bigl\|\lambdavec(\wh{S})\bigr\|_2^2 = \sum_{k = 1}^{n} \frac{1}{\bigl(1 + \rho \lambda_k\bigr)^2}.
\end{equation*} 
We deduce the following upper bound on the bias term,
\begin{equation*}
\begin{aligned}
\bigl\|(\wh{S} - I)f_0\bigr\|_2^2 & = f_0^{\top} \Lap^{1/2} \Lap^{-1/2}\bigl(\wh{S} - \Id\bigr) \Lap^{-1/2} \Lap^{1/2} f_0 \\
& \leq f_0^{\top} \Lap f_0 \cdot \lambda_n\Bigl(\Lap^{-1/2}\bigl(\wh{S} - \Id\bigr)\Lap^{-1/2}\Bigr) \\
& = f_0^{\top} \Lap f_0 \cdot \max_{k \in [n]} \biggl\{\frac{1}{\lambda_k} \Bigl(1 - \frac{1}{\rho\lambda_k + 1}\Bigr) \biggr\} \\
& = f_0^{\top} \Lap f_0 \cdot \rho.
\end{aligned}
\end{equation*} 
In the above, we have written $\Lap^{-1/2}$ for the square root of the pseudoinverse of $\Lap$, and the maximum is over all indices $k$ such that $\lambda_k > 0$. The claim of the Lemma then follows from Lemma~\ref{lem:linear_smoother_fixed_graph_estimation}.

\paragraph{Proof of Lemma~\ref{lem:ls_fixed_graph_testing}.}
Let $\wh{S} := (\rho \Lap + \Id)^{-1}$, and note that $\wh{T} = \frac{1}{n}{\bf Y}^{\top} \wh{S}^2 {\bf Y}$. The bound on Type I error~\eqref{eqn:ls_fixed_graph_testing_typeI} follows immediately from \eqref{eqn:linear_smoother_fixed_graph_testing_typeI}. 
To establish the bound on Type II error, we must lower bound $f_0^{\top} \wh{S}^2 f_0$. We first note that by assumption~\eqref{eqn:ls_fixed_graph_testing_critical_radius},
\begin{align*}
f_0^{\top} \wh{S}^2 f_0 & = \bigl\|f_0\bigr\|_2^2 - f_0^{\top}(I - \wh{S}^2)f_0 \\
& \geq 2 \rho \bigl(f_0^{\top} \Lap f_0\bigr) - f_0^{\top}\bigl(I - \wh{S}^2\bigr)f_0 + 4b \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{-1/2}.
\end{align*}
Upper bounding $f_0^{\top}\bigl(I - \wh{S}^2\bigr)f_0$ as follows:
\begin{equation*}
\begin{aligned}
f_0^{\top} \Bigl(\Id - \wh{S}^2\Bigr) f_0  & = f_0^{\top} \Lap^{1/2} \Lap^{-1/2}\Bigl(\Id - \wh{S}^2\Bigr) \Lap^{-1/2} \Lap^{1/2} f_0 \\ 
& \leq f_0^{\top} \Lap f_0 \cdot  \lambda_{n}\biggl(\Lap^{-1/2}\Bigl(\Id - \wh{S}^2\Bigr) \Lap^{-1/2}\biggr) \\ 
& \overset{(i)}{=}  f_0^{\top} \Lap f_0 \cdot \max_{k} \biggl\{ \frac{1}{\lambda_k} \Bigl(1 - \frac{1}{(\rho \lambda_k + 1)^2}\Bigr) \biggr\} \\
& \overset{(ii)}{\leq} f_0^{\top} \Lap f_0 \cdot 2\rho,
\end{aligned}
\end{equation*}
---where in the above the maximum is over all indices $k$ such that $\lambda_k > 0$, and the last inequality follows from the basic algebraic identity $1 - 1/(1 + x)^2 \leq 2 x$ for any $x > 0$---we deduce that
\begin{equation*}
f_0^{\top} \wh{S}^2 f_0 \geq 2b \biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \biggr)^{-1/2}.
\end{equation*} 
The upper bound on Type II error~\eqref{eqn:ls_fixed_graph_testing_typeII} then follows from Lemma~\ref{lem:linear_smoother_fixed_graph_testing}.

\section{Neighborhood graph Sobolev semi-norm}
\label{sec:graph_sobolev_seminorm}
In this section, we prove Lemma~\ref{lem:graph_sobolev_seminorm}, which states an upper bound on $f^{\top} \Lap_{n,r} f$ that holds when $f$ is bounded in Sobolev norm. We also establish stronger bounds in the case when $f$ has a bounded Lipschitz constant; this latter result justifies one of our remarks after Theorem~\ref{thm:laplacian_smoothing_estimation1}.

Throughout this proof, we will assume that $f \in H^1(\Xset)$ has zero-mean, meaning $\int_{\Xset} f(x) \,dx = 0$. This is without loss of generality---assuming for the moment that~\eqref{eqn:graph_sobolev_seminorm} holds for zero-mean functions, for any $f \in H^1(\Xset)$, taking $a = \int_{\Xset} f(x) \,dx$ and $g = f - a$, we have that
\begin{equation*}
f^{\top} L_{n,r} f = g^{\top} L_{n,r} g \leq \frac{C_2}{\delta} n^2 r^{d + 2} |g|_{H^1(\mc{X})}^2 = \frac{C_2}{\delta} n^2 r^{d + 2} |f|_{H^1(\mc{X})}^2.
\end{equation*} 
Now, for any zero-mean function $f \in H^1(\mc{X})$ it follows by the Poincare inequality (see Section 5.8, Theorem 1 of \citet{evans10}) that $\|f\|_{H^1(\mc{X})}^2 \leq C_8 |f|_{H^1(\mc{X})}^2$, for some constant $C_8$ that does not depend on $f$. Therefore, to prove Lemma~\ref{lem:graph_sobolev_seminorm}, it suffices to show that
\begin{equation*}
\Ebb\Bigl[f^{\top} \Lap_{n,r} f\Bigr] \leq C n^2 r^{d + 2} \|f\|_{H^1(\Xset)}^2,
\end{equation*}
since the high-probability upper bound then follows immediately by Markov's inequality. (Recall that $\Lap_{n,r}$ is positive semi-definite, and therefore $f^{\top} \Lap_{n,r} f$ is a non-negative random variable).

@@

Moreover, ignoring those cells for which $N(Q) = 0$ (since $\wt{P}_n(Q) = 0$ for such $Q$, and so they do not contribute to the essential supremum in~\eqref{eqn:optimal_transport}), appropriately dividing each remaining cell $Q \in \mc{Q}$ into $N(Q)$ subsets $S_1,\ldots,S_{N(Q)}$ of equal volume, and mapping each $S_{\ell}$ to a different design point $X_i \in Q$, we can exhibit a transport map $T$ from $\wt{P}_n$ to $P_n$ for which

@@

Noting that by assumption $P(\wt{Q}) \leq p_{\max} \vol(\wt{Q})$ and $\wt{\delta}^{-d} \leq n$, the claim follows upon plugging back into~\eqref{pf:prop_optimal_transport_3}, and setting

>>>>

\onecolumn	
\aistatstitle{Supplementary Material for ``Minimax Optimal Regression over
  Sobolev Spaces via Laplacian Regularization on Neighborhood Graphs''}

\aistatsauthor{Alden Green \And Sivaraman Balakrishnan \And Ryan J. Tibshirani}

\vspace{4pt}

\aistatsaddress{Carnegie Mellon University}

@@

Now we explain why the particular choice of representative is not crucial, using the notion of a Lebesgue point. Recall that for a locally Lebesgue integrable function $f$, a given point $x \in \mc{X}$ is a \emph{Lebesgue point} of $f$ if the limit of $1/(\nu(B(x,\varepsilon)))\int_{B(x,\varepsilon)} f(x) dx$ as $\varepsilon \to 0$ exists, and satisfies
\begin{equation*}
\lim_{\varepsilon \to 0} \frac{1}{\nu\bigl(B(x,\varepsilon)\bigr)} \int_{B(x,\varepsilon)} f(x) dx = f(x).
\end{equation*}
Let $E$ denote the set of Lebesgue points of $f$. By the Lebesgue differentiation theorem \citep{evans15}, if $f \in L^1(\mc{X})$ then almost every $x \in \mc{X}$ is a Lebesgue point, $\nu(\mc{X}\setminus E) = 0$. Since $f_0 \in H^1(\mc{X}) \subseteq \Leb^1(\mc{X})$, we can conclude that any function $g_0 \in f_0$ disagrees with the precise representative $f_0^{\star}$ only on a set of Lebesgue measure 0. Moreover, since we always assume the design distribution $P$ has a continuous density, with probability $1$ it holds that $g_0(X_i) = f_0^{\star}(X_i)$ for all $i = 1,\ldots,n$. This justifies the notation $f_0(X_i)$ used in the main text.

@@

\section{Graph-dependent error bounds}
\label{sec:fixed_graph_error_bounds}

In this section, we adopt the fixed design perspective; or equivalently, condition on $X_i = x_i$ for $i = 1,\ldots,n$. Let $G = \bigl([n],W\bigr)$ be a fixed graph on $\{1,\ldots,n\}$ with Laplacian matrix $\Lap = D - W$. The randomness thus all comes from the responses 
\begin{equation}
\label{eqn:fixed_graph_regression_model}
Y_i = f_{0}(x_i) + \varepsilon_i
\end{equation}
where the noise variables $\varepsilon_i$ are independent $N(0,1)$. In the rest of this section, we will mildly abuse notation and write $f_0 = (f_0(x_1),\ldots,f_0(x_n)) \in \Reals^n$. We will also write ${\bf Y} = (Y_1,\ldots,Y_n)$.

Recall \eqref{eqn:laplacian_smoothing} and \eqref{eqn:laplacian_smoothing_test}: the Laplacian smoothing estimator of $f_0$ on $G$ is
\begin{equation*}
\label{eqn:ls_G}
\wh{f} := \argmin_{f \in \Reals^n} \biggl\{ \sum_{i = 1}^{n}(Y_i - f_i)^2 + \rho \cdot f^{\top} \Lap f \biggr\} = (\rho \Lap + \Id)^{-1}{\bf Y}.
\end{equation*}
and the Laplacian smoothing test statistic is 
\begin{equation*}
\label{eqn:ls_ts_G}
\wh{T} := \frac{1}{n} \Bigl\|\wh{f}\Bigr\|_2^2.
\end{equation*}
We note that in this section, many of the derivations involved in upper bounding the estimation error of $\wh{f}$ are similar to those of \cite{sadhanala16}, with the difference being that we seek bounds in high probability rather than in expectation. We keep the work here self-contained for purposes of completeness.

\subsection{Error bounds for linear smoothers}

Let $S \in \Reals^{n \times n}$ be a square, symmetric matrix, and let 
\begin{equation*}
\wc{f} := SY
\end{equation*}
be a linear estimator of $f_0$. In  Lemma~\ref{lem:linear_smoother_fixed_graph_estimation} we upper bound the error $\frac{1}{n}\|\wc{f} - f_0\|_2^2$ as a function of the eigenvalues of $S$. Let $\lambdavec(S) = (\lambda_1(S),\ldots,\lambda_n(S)) \in \Reals^n$ denote these eigenvalues, and let $v_k(S)$ denote the corresponding unit-norm eigenvectors, so that $S = \sum_{k = 1}^{n} \lambda_k(S) \cdot v_k(S) v_k(S)^{\top}$. Denote $Z_k = v_k(S)^{\top} \varepsilon$, and observe that ${\bf Z} = (Z_1,\ldots,Z_n) \sim N(0,\Id)$.

@@

\textit{Variance.} Starting from \eqref{pf:linear_smoother_fixed_graph_testing1} and recalling $\Var(Z_k^2) = 2$, we derive
\begin{equation}
\label{pf:linear_smoother_fixed_graph_testing_var}
\Var_{f_0}\bigl[\wc{T}\bigr] \leq 8 f_0^{\top} S^4 f_0 + 4 \sum_{k = 1}^{n} \bigl(\lambda_k(S)\bigr)^4.
\end{equation}

\textit{Bounding Type I and Type II error.} The upper bound \eqref{eqn:linear_smoother_fixed_graph_testing_typeI} follows immediately from \eqref{pf:linear_smoother_fixed_graph_testing_mean}, \eqref{pf:linear_smoother_fixed_graph_testing_var}, and Chebyshev's inequality.

The bound \eqref{eqn:linear_smoother_fixed_graph_testing_typeII} also follows from Chebyshev's inequality, as can be seen by the following manipulations,
\begin{equation*}
\begin{aligned}
\Pbb_{f_0}\Bigl(\wc{T} \leq \wc{t}_b\Bigr) & = \Pbb_{f_0}\Bigl(\wc{T} - \Ebb_{f_0}\bigl[\wc{T}\bigr] \leq \wc{t}_b - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr) \\
& \overset{(i)}{\leq} \Pbb_{f_0}\Bigl(\Bigl|\wc{T} - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr| \geq \Bigl|\wc{t}_b - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr|\Bigr) \leq \frac{Var_{f_0}\bigl[\wc{T}\bigr]}{\bigl(\wc{t}_b - \Ebb_{f_0}\bigl[\wc{T}\bigr]\bigr)^2} \\ 
& \overset{(ii)}{\leq} 4 \frac{\Var_{f_0}\bigl[\wc{T}\bigr]}{(f_0^{\top} S^2 f_0)^2} \\
& \overset{(iii)}{\leq} \frac{32}{f_0^{\top} S^2 f_0} + \frac{4}{b^2} \\
& \overset{(iv)}{\leq} \frac{8}{b} \Biggl(\sum_{k = 1}^{n}\bigl(\lambda_k(S)\bigr)^4\Biggr)^{-1/2} + \frac{4}{b^2}
\end{aligned}
\end{equation*}
In the previous expression, $(i)$ and $(ii)$ follow since assumption \eqref{eqn:linear_smoother_fixed_graph_testing_critical_radius} and equation \eqref{pf:linear_smoother_fixed_graph_testing_mean} together imply 
\begin{equation*}
\wc{t}_b - \Ebb_{f_0}[\wc{T}] = f_0^{\top} S^2 f_0 - 2b\|{\bf \lambda}(S)\|_4^2 \geq \frac{1}{2}f_0^{\top} S^2 f_0
\end{equation*}
$(iii)$ follows from assumption \eqref{eqn:linear_smoother_fixed_graph_testing_critical_radius} and the inequality \eqref{pf:linear_smoother_fixed_graph_testing_var}, and $(iv)$ follows from \eqref{eqn:linear_smoother_fixed_graph_testing_critical_radius}.

\subsection{Analysis of Laplacian smoothing}

Upper bounds on the mean squared error of $\wh{f}$, and Type I and Type II error of $\wh{T}$, follow from setting $S = (\rho L + I)^{-1}$ in Lemmas~\ref{lem:linear_smoother_fixed_graph_estimation} and~\ref{lem:linear_smoother_fixed_graph_testing}. We give these results in Lemma~\ref{lem:ls_fixed_graph_estimation} and~\ref{lem:ls_fixed_graph_testing}, and prove them immediately. Recall that $\lambda_1,\ldots,\lambda_n$ are the $n$ eigenvalues of $\Lap$ (sorted in ascending order).
\begin{lemma}
	\label{lem:ls_fixed_graph_estimation}
	For any $\rho > 0$,
	\begin{equation}
	\label{eqn:ls_fixed_graph_estimation_prob}
	\frac{1}{n}\bigl\|\wh{f} - f_0\bigr\|_2^2 \leq \frac{2\rho}{n} \bigl(f_0^{\top} \Lap f_0\bigr) + \frac{10}{n}\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_{k} + 1\bigr)^2}
	\end{equation}
	with probability at least $1 - \exp\Bigl(-\sum_{k = 1}^{n}\bigl(\rho \lambda_k + 1\bigr)^{-2}\Bigr)$.
\end{lemma}
Recall that 
\begin{equation*}
\wh{t}_b := \frac{1}{n}\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k + 1\bigr)^2} + \frac{2b}{n}\sqrt{\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k + 1\bigr)^4}}.
\end{equation*}
\begin{lemma}
	\label{lem:ls_fixed_graph_testing}
	For any $\rho > 0$ and any $b \geq 1$, it holds that:
	\begin{itemize}
		\item \textbf{Type I error.}
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_typeI}
		\Pbb_0\Bigl(\wh{T} > \wh{t}_b\Bigr) \leq \frac{1}{b^2}
		\end{equation}
		\item \textbf{Type II error.} If
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_critical_radius}
		\frac{1}{n}\norm{f_0}_2^2 \geq \frac{2 \rho}{n} \bigl(f_0^{\top} \Lap f_0\bigr) + \frac{4b}{n} \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{1/2}
		\end{equation}
		then
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_typeII}
		\Pbb_{f_0}\Bigl(\wh{T}(G) \leq \wh{t}_b\Bigr) \leq \frac{4}{b^2} + \frac{8}{b} \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{-1/2}
		\end{equation}
	\end{itemize}
\end{lemma}

\paragraph{Proof of Lemma~\ref{lem:ls_fixed_graph_estimation}.}
Let $\wh{S} = (\Id + \rho \Lap)^{-1}$, the estimator $\wh{f} = \wh{S}Y$, and
\begin{equation*}
\bigl\|\lambdavec(\wh{S})\bigr\|_2^2 = \sum_{k = 1}^{n} \frac{1}{\bigl(1 + \rho \lambda_k\bigr)^2}.
\end{equation*} 
We deduce the following upper bound on the bias term,
\begin{equation*}
\begin{aligned}
\bigl\|(\wh{S} - I)f_0\bigr\|_2^2 & = f_0^{\top} \Lap^{1/2} \Lap^{-1/2}\bigl(\wh{S} - \Id\bigr) \Lap^{-1/2} \Lap^{1/2} f_0 \\
& \leq f_0^{\top} \Lap f_0 \cdot \lambda_n\Bigl(\Lap^{-1/2}\bigl(\wh{S} - \Id\bigr)\Lap^{-1/2}\Bigr) \\
& = f_0^{\top} \Lap f_0 \cdot \max_{k \in [n]} \biggl\{\frac{1}{\lambda_k} \Bigl(1 - \frac{1}{\rho\lambda_k + 1}\Bigr) \biggr\} \\
& = f_0^{\top} \Lap f_0 \cdot \rho.
\end{aligned}
\end{equation*} 
In the above, we have written $\Lap^{-1/2}$ for the square root of the pseudoinverse of $\Lap$, and the maximum is over all indices $k$ such that $\lambda_k > 0$. The claim of the Lemma then follows from Lemma~\ref{lem:linear_smoother_fixed_graph_estimation}.

\paragraph{Proof of Lemma~\ref{lem:ls_fixed_graph_testing}.}
Let $\wh{S} := (\rho \Lap + \Id)^{-1}$, and note that $\wh{T} = \frac{1}{n}{\bf Y}^{\top} \wh{S}^2 {\bf Y}$. The bound on Type I error \eqref{eqn:ls_fixed_graph_testing_typeI} follows immediately from \eqref{eqn:linear_smoother_fixed_graph_testing_typeI}. 
To establish the bound on Type II error, we must lower bound $f_0^{\top} \wh{S}^2 f_0$. We first note that by assumption \eqref{eqn:ls_fixed_graph_testing_critical_radius},
\begin{align*}
f_0^{\top} \wh{S}^2 f_0 & = \bigl\|f_0\bigr\|_2^2 - f_0^{\top}(I - \wh{S}^2)f_0 \\
& \geq 2 \rho \bigl(f_0^{\top} \Lap f_0\bigr) - f_0^{\top}\bigl(I - \wh{S}^2\bigr)f_0 + 4b \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{-1/2}.
\end{align*}
Upper bounding $f_0^{\top}\bigl(I - \wh{S}^2\bigr)f_0$ as follows:
\begin{equation*}
\begin{aligned}
f_0^{\top} \Bigl(\Id - \wh{S}^2\Bigr) f_0  & = f_0^{\top} \Lap^{1/2} \Lap^{-1/2}\Bigl(\Id - \wh{S}^2\Bigr) \Lap^{-1/2} \Lap^{1/2} f_0 \\ 
& \leq f_0^{\top} \Lap f_0 \cdot  \lambda_{n}\biggl(\Lap^{-1/2}\Bigl(\Id - \wh{S}^2\Bigr) \Lap^{-1/2}\biggr) \\ 
& \overset{(i)}{=}  f_0^{\top} \Lap f_0 \cdot \max_{k} \biggl\{ \frac{1}{\lambda_k} \Bigl(1 - \frac{1}{(\rho \lambda_k + 1)^2}\Bigr) \biggr\} \\
& \overset{(ii)}{\leq} f_0^{\top} \Lap f_0 \cdot 2\rho,
\end{aligned}
\end{equation*}
---where in the above the maximum is over all indices $k$ such that $\lambda_k > 0$, and the last inequality follows from the basic algebraic identity $1 - 1/(1 + x)^2 \leq 2 x$ for any $x > 0$---we deduce that
\begin{equation*}
f_0^{\top} \wh{S}^2 f_0 \geq 2b \biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \biggr)^{-1/2}.
\end{equation*} 
The upper bound on Type II error \eqref{eqn:ls_fixed_graph_testing_typeII} then follows from Lemma~\ref{lem:linear_smoother_fixed_graph_testing}.

\section{Neighborhood graph Sobolev semi-norm}
\label{sec:graph_sobolev_seminorm}

In this section, we prove Lemma~\ref{lem:graph_sobolev_seminorm}, which states an upper bound on $f^{\top} \Lap_{n,r} f$ that holds when $f$ is bounded in Sobolev norm. We also establish stronger bounds in the case when $f$ has a bounded Lipschitz constant; this latter result justifies one of our remarks after Theorem~\ref{thm:laplacian_smoothing_estimation1}.

Throughout this proof, we will assume that $f \in H^1(\Xset)$ has zero-mean, meaning $\int_{\Xset} f(x) \,dx = 0$. This is without loss of generality---assuming for the moment that \eqref{eqn:graph_sobolev_seminorm} holds for zero-mean functions, for any $f \in H^1(\Xset)$, taking $a = \int_{\Xset} f(x) \,dx$ and $g = f - a$, we have that
\begin{equation*}
f^{\top} L_{n,r} f = g^{\top} L_{n,r} g \leq \frac{C_2}{\delta} n^2 r^{d + 2} |g|_{H^1(\mc{X})}^2 = \frac{C_2}{\delta} n^2 r^{d + 2} |f|_{H^1(\mc{X})}^2.
\end{equation*} 
Now, for any zero-mean function $f \in H^1(\mc{X})$ it follows by the Poincare inequality (see Section 5.8, Theorem 1 of \citet{evans10}) that $\|f\|_{H^1(\mc{X})}^2 \leq C_8 |f|_{H^1(\mc{X})}^2$, for some constant $C_8$ that does not depend on $f$. Therefore, to prove Lemma~\ref{lem:graph_sobolev_seminorm}, it suffices to show that
\begin{equation*}
\Ebb\Bigl[f^{\top} \Lap_{n,r} f\Bigr] \leq C n^2 r^{d + 2} \|f\|_{H^1(\Xset)}^2,
\end{equation*}
since the high-probability upper bound then follows immediately by Markov's inequality. (Recall that $\Lap_{n,r}$ is positive semi-definite, and therefore $f^{\top} \Lap_{n,r} f$ is a non-negative random variable).

@@

Moreover, ignoring those cells for which $N(Q) = 0$ (since $\wt{P}_n(Q) = 0$ for such $Q$, and so they do not contribute to the essential supremum in \eqref{eqn:optimal_transport}), appropriately dividing each remaining cell $Q \in \mc{Q}$ into $N(Q)$ subsets $S_1,\ldots,S_{N(Q)}$ of equal volume, and mapping each $S_{\ell}$ to a different design point $X_i \in Q$, we can exhibit a transport map $T$ from $\wt{P}_n$ to $P_n$ for which

@@

Noting that by assumption $P(\wt{Q}) \leq p_{\max} \vol(\wt{Q})$ and $\wt{\delta}^{-d} \leq n$, the claim follows upon plugging back into \eqref{pf:prop_optimal_transport_3}, and setting
